---
title: "R Notebook"
output: html_notebook
---

## Installing Packages

```{r}
library(tidyverse)
library(caret)
library(dslabs)
library(dplyr)
library(lubridate)

```

## Comprehension Check: Practice with Machine Learning, Part 1

### The code below sets up the dataset to analyze in the following exercises:

```{r}

dat <- mutate(reported_heights, date_time = ymd_hms(time_stamp)) %>%
  filter(date_time >= make_date(2016, 01, 25) & date_time < make_date(2016, 02, 1)) %>%
  mutate(type = ifelse(day(date_time) == 25 & hour(date_time) == 8 & between(minute(date_time), 15, 30), "inclass","online")) %>%
  select(sex, type)

y <- factor(dat$sex, c("Female", "Male"))
x <- dat$type

```

### Q1 

The type column of dat indicates whether students took classes in person ("inclass") or online ("online"). What proportion of the inclass group is female? What proportion of the online group is female?

```{r}

dat %>%
  group_by(type) %>%
  summarize(prop_female = mean(sex == "Female"))

```

### Q2

In the course videos, height cutoffs were used to predict sex. Instead of height, use the type variable to predict sex. Assume that for each class type the students are either all male or all female, based on the most prevalent sex in each class type you calculated in Q1. Report the accuracy of your prediction of sex based on type. You do not need to split the data into training and test sets.

```{r}

y_hat <- ifelse(x == "online", "Male", "Female") %>% 
  factor(levels  = levels(y)) 
mean(y == y_hat) # accuracy

```

### Q3

Confussion Matrix

```{r}
table(y_hat,y)
```
### Q4 Q5 Q6

What is the sensitivity of this prediction? You can use the sensitivity() function from the caret package. specificity? prevalience of female in dat?

```{r}
sensitivity(y_hat, y)

specificity(y_hat, y)

mean(y == "Female")

```
## Comprehension Check: Practice with Machine Learning, Part 2

